Suppl. Figure 5. Rarefaction curves

### 2022-02-10 reports/manuscript/Figure4-5.Rmd
Move files one lvl up

---
title: "DGE's and Enrichment"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

###########################
# ASSEMBLE PLOTS FUNCTION #
###########################
arrange_plots.fun <- function(degs, group, gr_name, comparison, enrichment_db, file, Layout){

@@

```{r Figure 4., message=FALSE, warning=FALSE, echo=FALSE, fig.height=6}
# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )
#layout.show(layout(l[[1]],l[[2]],l[[3]]))

@@

# test figure
dev.copy2pdf(file=paste0("./test.pdf"),
    width = 6.6,
    height = 6, paper = "a4"
    )
```

```{r Figure 5., message=FALSE, warning=FALSE, echo=FALSE, fig.height=6}
# comparison <- sheets
# enrichment_db <- "TF_PPI_enrichment"
# degs <- enrich_T
# group <- "Tissue_gr" 
# gr_name <- "Tissue"

# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )

@@

dev.copy2pdf(file=paste0("./test.pdf"),
    width = 6.6,
    height = 6, paper = "a4"
    )
```

>>>>

---
title: "DGE's and Enrichment"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(scales)
  library(RColorBrewer)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(readxl)
  library(enrichR)
  library(igraph)
  library(rafalib)
})  })  })

@@

###########################
# ASSEMBLE PLOTS FUNCTION #
###########################
# comparison <- sheets
# enrichment_db <- "TF_PPI_enrichment"
# degs <- enrich_T
# group <- "Tissue_gr" 
# gr_name <- "Tissue"
arrange_plots.fun <- function(degs, group, gr_name, comparison, enrichment_db, file, Layout){

@@

```{r Figure 4, message=FALSE, warning=FALSE, echo=FALSE, fig.height=6}
# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )
#layout.show(layout(l[[1]],l[[2]],l[[3]]))

@@

# test figure
# dev.copy2pdf(file=paste0("./test.pdf"),
#     width = 6.6,
#     height = 6, paper = "a4"
#     )
```

```{r Figure 5, message=FALSE, warning=FALSE, echo=FALSE, fig.height=6}
# Layout
l <- list(mat = matrix(c(1,2,3,4,4,4,5,5,5,
                         1,2,3,4,4,4,5,5,5,
                         6,6,6,7,7,8,8,9,9,
                         10,10,10,11,11,12,12,13,13),
                nrow = 3,ncol = 9,byrow = T),
          widths = c(1.14,3.5,.36,2.5,2.5,2.5,2.5,2.5,2.5),
          heigth = c(1,1,1.5)
          )

@@

# dev.copy2pdf(file=paste0("./test.pdf"),
#     width = 6.6,
#     height = 6, paper = "a4"
#     )
```

### 2022-02-10 reports/manuscript/Figure6.Rmd
Move files one lvl up

---
title: "Figure 6. Differential Protein expression"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

#############
# LODA DATA #
#############
Protein_V3 <- read_csv("../../../data/2020_04_20_LAMIQ_visit_3_singlets.csv") 
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1, stringsAsFactors = F)
cytokine_data <- read.csv("../../../data/210125_Cytokines_visit3CVL.csv")

#color palettes
#################
# COLOR PALETTS #
#################
pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
```

@@

```{r Figure 6., echo = FALSE, eval = TRUE, fig.height=10, fig.width=7}
figlabels <- letters

# top differentially expressed proteins Luminal groups
t <- top_dpe.fun(dpe_L$top)
plot_heatmap.fun(t, "Luminal_gr", scale = T, layout = "multi")

# top differentially expressed proteins Tissue groups
t <- top_dpe.fun(dpe_T$top)
par(mfg = c(2,1)) # adds the remaning plots to the previous layout
plot_heatmap.fun(t, "Tissue_gr", scale = T)

# Luminal Cytokine plot 
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
stars <- Luminal$stars_df

@@

# Tissue Cytokine plot
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
stars <- Tissue$stars_df

>>>>

---
title: "Figure 6. Differential Protein expression"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(edgeR)
  library(openxlsx)
  library(rstatix)
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
})  })  })

#############
# LODA DATA #
#############
datasets_all_samples <- readRDS("../../../results/datasets_all_samples.RDS")
Protein_V3 <- read_csv("../../../data/2020_04_20_LAMIQ_visit_3_singlets.csv")
cytokine_data <- read.csv("../../../data/210125_Cytokines_visit3CVL.csv")
metadata <- read.csv2("../../../results/metadata_integration.csv",row.names = 1, stringsAsFactors = F)

#################
# COLOR PALETTS #
#################
pal <- c( "#0072B2", "#009E73","#D55E00", "#CC79A7", "#E69F00", "#999999")
taxa_pal <- c(RColorBrewer::brewer.pal(8,"Pastel2"),RColorBrewer::brewer.pal(8,"Pastel1"),"grey90")
```

@@

```{r Figure 6, echo = FALSE, eval = TRUE, fig.height=10, fig.width=7}
figlabels <- letters
####################################
# TOP DIFF. EXPRESSED PROT HEATMAP #
####################################
### A
# Luminal groups
t <- top_dpe.fun(dpe_L$top)
plot_heatmap.fun(t, "Luminal_gr", scale = T, layout = "multi")

### C
# Tissue groups
t <- top_dpe.fun(dpe_T$top)
par(mfg = c(2,1)) # adds the remaning plots to the previous layout
plot_heatmap.fun(t, "Tissue_gr", scale = T)

##############################
# SIG. CYTOKINES VIOLIN PLOT #
##############################
### B
# Luminal groups
g <- c("IL1a", "MIG", "IP10", "IL1b", "IL12_p70", "MCP1")
Luminal <- sig_stars.fun(s$Kruskal_Luminal_gr, s$`Dunn's_Luminal_gr`, "Luminal_gr", order = g)
stars <- Luminal$stars_df

@@

### D
# Tissue groups
Tissue <- sig_stars.fun(s$Kruskal_Tissue_gr, s$`Dunn's_Tissue_gr`, "Tissue_gr")
stars <- Tissue$stars_df

### 2022-02-10 reports/manuscript/Suppl.Figure2.Rmd
Move files one lvl up

---
title: "Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r echo=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Suppl. Figure 9, eval=T,warning=FALSE, message=FALSE,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

figlabels <- letters
par(mfrow=c(1,2),mar=c(2,12,1,3.1))
plot_dots( all_microbiome, genes = names(sort(ord)) , clustering = datasets,
           show_grid = T,cex.main=1,font.main=1,
           cex.row = .8,cex.col = .8,srt = 0)
add_letter("a")
barlist( all_microbiome, names(sort(ord)) , clustering = datasets,
         show_grid = T,cex.main=1,font.main=1,
         cex.axis = .8,srt = 0)
add_letter("b")

>>>>

---
title: "Suppl. Figure 2. Differential bacterial abundance across Tissue and Luminal microbiome"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r echo=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  #remotes::install_github("czarnewski/niceRplots",force=T)
  library(niceRplots)
  library(openxlsx)
})  })  })

@@

```{r Suppl.Fig.2 Diff_bact_abundance, eval=T,warning=FALSE, message=FALSE,echo = FALSE,fig.width=10,fig.height=9}
all_microbiome <- cbind(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]],
                        datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])
datasets <- factor(c( rep("Tissue",ncol(datasets_all_samples[["ASV_tissue_V3_normalized_batch_corrected"]])) , rep("Luminal",ncol(datasets_all_samples[["ASV_CVL_V3_normalized_batch_corrected"]])) ))
datasets <- datasets[ colSums(all_microbiome)>0 ]
all_microbiome <- all_microbiome[,colSums(all_microbiome)>0]

@@

### A & B
####################################
# DIFFERENTIAL BACTERIAL ABUNDANCE #
####################################
figlabels <- letters
par(mfrow=c(1,2),mar=c(2,12,1,3.1))
plot_dots( all_microbiome, genes = names(sort(ord)) , clustering = datasets,
           show_grid = T,cex.main=1,font.main=1,
           cex.row = .8,cex.col = .8,srt = 0)
add_letter("a")
barlist( all_microbiome, names(sort(ord)) , clustering = datasets,
         show_grid = T,cex.main=1,font.main=1,
         cex.axis = .8,srt = 0)
add_letter("b")

### 2022-02-10 reports/manuscript/Suppl.Figure5.Rmd
Move files one lvl up

---
title: "Suppl. Figure 5. Rarefaction curves"
output: 
  pdf_document:
    fig_caption: yes
    keep_tex: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(vegan)
  library(phyloseq)
  library(ggpubr)
})  })  })

@@

```{r Print rare curves, warning=FALSE, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.asp=0.75,}
plot <- ggarrange(
          #rare_plot[[1]] + theme(axis.title.x=element_blank(),plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          #rare_plot[[3]] + theme(axis.title.x=element_blank()),
          rare_plot[[4]] + theme(axis.title.x=element_blank(), plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          rare_plot[[6]] + theme(plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          ncol = 1,
          labels = c("a","b","c","d")
          )
print(plot)

>>>>

---
title: "Suppl. Figure 5. Rarefaction curves"
output: 
  pdf_document:
    fig_caption: yes
header-includes: 
- \usepackage{float}
editor_options: 
  chunk_output_type: console
---

```{r setup}
knitr::opts_chunk$set(
  fig.path="./Figures/",
  fig.process = function(filename){
    new_filename <- stringr::str_remove(string = filename, 
                                        pattern = "-1")
    fs::file_move(path = filename, new_path = new_filename)
    ifelse(fs::file_exists(new_filename), new_filename, filename)
})
#setwd("/Users/vilkal/work/Brolidens_work/Projects/Gabriella_repo/reports/rmarkdown/manuscript")
```

```{r message=FALSE, warning=FALSE, include=FALSE}
##################
# LOAD LIBRARIES #
##################
suppressWarnings({suppressMessages({suppressPackageStartupMessages({
  library(tidyverse)
  library(vegan)
  library(phyloseq)
  library(ggpubr)
})  })  })

@@

```{r Suppl.Fig5 Rarefraction_plot, warning=FALSE, echo=FALSE, fig.align="center", fig.height=6, fig.width=8, fig.asp=0.75,}
### A & B
###########################
# RAREFRACTION CURVE PLOT #
###########################
plot <- ggarrange(
          #rare_plot[[1]] + theme(axis.title.x=element_blank(),plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          #rare_plot[[3]] + theme(axis.title.x=element_blank()),
          rare_plot[[4]] + theme(axis.title.x=element_blank(), plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          rare_plot[[6]] + theme(plot.margin=unit(c(.5,.5,.5,.5),"cm")),
          ncol = 1,
          labels = c("a","b","c","d")
          )
print(plot)
